\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{margin=1in}

\begin{document}

\begin{center}
    {\LARGE \textbf{Xin He}} \\[6pt]
    University of Science and Technology of China (USTC), School of Management \\
    Hefei, China \\
    \href{https://www.xinhesean.com}{www.xinhesean.com} \\
\end{center}

---

\section*{Employment}
\begin{itemize}[leftmargin=*]
    \item 2024--Present: Tenure-Track Associate Professor of Finance, USTC.
    \item 2022--2024: Assistant Professor, College of Finance and Statistics, Hunan University.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item Ph.D., Management Sciences, City University of Hong Kong, 2018--2022. Advisors: Prof. Guanhao Feng, Prof. Junbo Wang.
    \item B.S., Industrial Engineering, Shanghai Jiao Tong University, 2014--2018.
\end{itemize}

\section*{Research Interests}
Asset Pricing; Quantamental Investment.

\section*{Publications}
\begin{enumerate}[leftmargin=*]
    \item \emph{Growing the Efficient Frontier on Panel Trees} (with Lin William Cong, Guanhao Feng, Jingyu He). Journal of Financial Economics, 2025.
    \item \emph{Predicting Individual Corporate Bond Returns} (with Guanhao Feng, Yanchu Wang, Chunchi Wu). Journal of Banking \& Finance, 2025.
    \item \emph{The Bright Side of Cross Ownership: Evidence From the Corporate Resilience to COVID-19 Crisis in China} (with Yihui Chen, Haoyuan Wei). International Review of Finance, 2025.
\end{enumerate}

\section*{Working Papers}
\begin{itemize}[leftmargin=*]
    \item Stochastic Discount Factors with Cross-Asset Spillovers (with Doron Avramov), 2025.
    \item Panel Tree Benchmarks for Corporate Bond Returns and Mutual Fund Evaluation, 2025.
    \item Portfolio Optimization with Panel Trees, 2025.
    \item Factor Investing and the Integration of Equity and Corporate Bond Markets, 2025.
    \item Firm Engagement in Belt and Road Initiative and the Cross-Section of Stock Returns, 2024.
    \item The Risk of Finance Words, 2024.
    \item Benchmarking Individual Corporate Bonds, 2024.
\end{itemize}

\section*{Grants and Awards}
\begin{itemize}[leftmargin=*]
    \item IQAM Research Award, 2024.
    \item INQUIRE Europe Research Grant, 2022.
    \item Best Paper Award (Corporate Finance \& Accounting), 10th Jingshi Scholar Forum.
    \item Outstanding Advisor, Hunan University.
\end{itemize}

\section*{Teaching Experience}
\begin{itemize}[leftmargin=*]
    \item Empirical Asset Pricing.
    \item Financial Engineering \& Advanced Topics.
    \item Fixed-Income Securities (Evaluation: 98/100).
    \item Behavioral Finance (Evaluation: 97.7/100).
    \item Simulation \& Experiments in Financial Engineering.
\end{itemize}

\section*{Service and Skills}
\begin{itemize}[leftmargin=*]
    \item Referee: Journal of Banking \& Finance, Journal of Empirical Finance, Journal of Financial Markets.
    \item Programming: Python, R, MATLAB, C++, SAS.
    \item Databases: CRSP, Compustat, IBES, TRACE, Wind, CSMAR.
\end{itemize}

\end{document}
