%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Chinese Character



% Increase text height
\textheight=700pt

\usepackage{hyperref}
\hypersetup{colorlinks, linkcolor={green},citecolor={red},urlcolor={blue}}  

\usepackage{xcolor}
%\newcommand\updateinfo{\color{black} Updated on \today}
\usepackage{datetime}
\newdateformat{monthyeardate}{%
	\monthname[\THEMONTH], \THEYEAR}

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
%\name{Xin HE (Sean)}
%\address{\today}

\name{Xin HE}
\address{\monthyeardate\today}


% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

%\address{
%7/F, Lau Ming Wai Academic Building\\
%83 Tat Chee Avenue, Kowloon Tong\\
%Hong Kong, China
%}
%\address{xin.he@my.cityu.edu.hk \\ https://xinhe97.github.io\\ \updateinfo \\}


% Uncomment to add a third address
% \address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------

%\section{\sc Contact Information}

%\begin{tabular}{@{}p{2.75in}p{.85in}p{3in}}
%	Floor 7, Lau Ming Wai Academic Building	   & \textit{E-mail:}       & xin.he@my.cityu.edu.hk\\        
%	83 Tat Chee Avenue, Kowloon Tong 			& \textit{Webpage:}    & https://xinhe.netlify.com \\
%	Hong Kong SAR, China  								& \textit{Last update:} & \today \\
%\end{tabular}

\section{\sc Contact Information}
	No.3 Building, 109th Shijiachong Road	   \hfill xinh@hnu.edu.cn\\        
	Yuelu, Changsha, Hunan, China 	\hfill   \url{https://www.xinhesean.com} \\

\vspace{5mm}

\section{\sc Employment}
\textbf{Hunan University, College of Finance and Statistics}\\
{Assistant Professor of Finance, 2022-Present}\\

\vspace{5mm}

\section{\sc Education}
\textbf{City University of Hong Kong}\\
{Ph.D. in Statistics and Finance, 2018 - 2022}\\
Advisors: Professor Guanhao Feng and Professor Junbo Wang

\textbf{Shanghai Jiao Tong University}\\
{B.S. in Industrial Engineering and Management, 2014 - 2018}

\vspace{5mm}

\section{\sc Research Interests}
{Machine Learning in Finance, FinTech, Empirical Asset Pricing}

%\vspace{5mm}
%
%\section{\sc Publication and \\ Accepted Paper}

\vspace{5mm}

\section{\sc Working \\ Paper}

\textbf{Benchmarking Individual Corporate Bonds \\}
with Guanhao Feng, Junbo Wang, and Chunchi Wu.  June. 2022.

\textbf{Asset Pricing with Panel Trees Under Global Split Criteria \\}
with Lin William Cong, Guanhao Feng, and Jingyu He. Apr. 2022. 

\textbf{Predicting Individual Corporate Bond Returns \\}
with Guanhao Feng, Junbo Wang, and Chunchi Wu. Jun. 2021.


\vspace{5mm}

%\section{\sc Work in \\ Progress}

%\textbf{Earnings Nowcast and Earnings Surprise \\}
%Preliminary.

\section{\sc Research Grants}

	\normalfont{Co-I: 
		General Research Fund at HKRGC for
		``Regression Tree for Portfolio Optimization and Imbalanced Data''.  % about 500k HKD
		2023-2025}\\
	\normalfont{Co-I: 
		Research Grant at INQUIRE Europe for
		``P-Trees: A New Interpretable Framework For Asset Pricing and Investment Management''.  % about 10k EURO
		2022-2024}\\
	\normalfont{Co-I: 
		General Research Fund at HKRGC for
		``Textual Analysis of Corporate Bond Market''.  % about 700k HKD
		2022-2024}\\

\vspace{5mm}

\section{\sc Honors and Awards}

\normalfont{INQUIRE Europe Research Grant Award. 2022\\}
\normalfont{Best Paper Award, Graduate Student Forum on Economics \& Finance, Antai College, Shanghai Jiao Tong University. 2021\\}
\normalfont{College of Business PhD Student Conference Grant, City University of Hong Kong. 2021\\}
\normalfont{Ph.D. Studentship, City University of Hong Kong. 2018 - 2022\\}
\normalfont{Second Prize, National Contest of Industrial Engineering Applications, Tsinghua University 2016\\}
\normalfont{Academic Excellence Award, Shanghai Jiao Tong University. 2015, 2016, 2017\\}

%\vspace{5mm}

\section{\sc Teaching Experience}

\textit{Tutorial:} \\
\normalfont{Business Statistics. 20/21, 21/22\\} 
\normalfont{Statistical Modeling in Finance and Economics. 19/20\\}
\\
\textit{Teaching Assistant:} \\
\normalfont{Business Statistics. 21/22\\} 
\normalfont{Stochastic Operations Research. 19/20\\}
\normalfont{Statistical Modeling in Marketing. 18/19, 19/20\\}
\normalfont{Statistical Modeling in Finance and Economics. 18/19, 19/20\\}
\normalfont{Operations Management. 18/19\\}

%\vspace{5mm}

\section{\sc Academic Service}

\textit{Ad Hoc Referee:}  \\
%Journals: \\
Annals of Operations Research,
Asia-Pacific Journal of Accounting and Economics,
Econometrics and Statistics, 
Quantitative Finance,
%\\
Applied Sciences,
Econometrics,
Economies, 
Information,
International Journal of Financial Studies,
Journal of Risk and Financial Management,
Sustainability,
Transactions on Intelligent Systems and Technology.

\textit{Program Committee:} \\
2022 FMA Annual Meeting

\textit{Session Chair:}  \\
2022 INFORMS Annual Meeting Indianapolis, “Machine Learning in Finance”

\vspace{5mm}

\section{\sc Presentations}

\textit{2022} \\
Australasian Finance \& Banking Conference, University of New South Wales (2022/12, Sydney) \\
China International Risk Forum, Dongbei University of Finance and Economics  (2022/7, Online) \\
Asian Meeting of the Econometric Society in China, CUHK(SZ) (2022/6, Online) \\
6th PKU-NUS Annual International Conference on Quantitative Finance and Economics, National University of Singapore (2022/5, Online) \\

\textit{2021} \\
Hong Kong Machine Learning Meetup (2021/12, Online) \\
China Finance Annual Meeting, Xiamen University (2021/10, Online) \\
INFORMS Annual Meeting (2021/10, Online) \\
Financial Management Association Annual Meeting (2021/10, Online) \\
Seminar, City University of Hong Kong (2021/9, Hong Kong) \\
SoFiE Financial Econometrics Summer School "Machine Learning in Finance", NYU Shanghai (2021/8, Online) \\
China International Risk Forum, Southwestern University of Finance and Economics  (2021/7, Chengdu) \\
37th International Conference of the French Finance Association, Audencia Business School (2021/5, Online) \\
4th China Accounting and Finance Conference, Sichuan University (2021/4, Online) \\
Financial Markets and Corporate Governance Conference, La Trobe University (2021/4, Online) \\
Camphor Economic Society Seminar Beijing (2021/2, Online) \\
Camphor Economic Society Seminar Fujian (2021/1, Online)\\

%\vspace{5mm}

\section{\sc Discussion}

``Corporate Bond Pricing Using Interpretable and Arbitrage-Free Deep Learning'' at CIRF  (2022/7, Online)
\\
``Manager Uncertainty and the Cross-Section of Stock Returns'' at FMA Annual Conference (2021/10, Online)
\\
``Does Reputation Matter? Evidence on Spatial Competition in China’s Bond Market" at Financial Markets and Corporate Governance Conference (2021/5, Online)
\\
``How should we measure the performance of corporate bond mutual funds? Evaluating model quality and impact on inferences'' at FMA Annual Conference (2020/10, Online)
\\


\section{\sc Miscellaneous}

Programming : Python, R, MATLAB, SAS, Linux, SQL
\\
Database : CRSP, Compustat, IBES, TRACE, FISD, Wind
\\
Hobby: playing sports (go, soccer, basketball) and reading (geograghy, philosophy)
%\\
%WorldQuant University : Data Science Module Unit I \& II with Honors, Master in Financial Engeneering course work in progress

%-------------------------------------------------------------------------------


\end{resume}
\(\)\end{document}