\documentclass{clean_cv}

% Add a BibTeX-style file encoding all of your publications to include here. You can export this from Zotero. Only include
% publications you want to appear here!
\addbibresource{publications.bib}
\usepackage{etaremune}

\author{Xin He}
\headlineposition{}

\begin{document}

\maketitle
% In this section, you can use any of the FontAwesome icons. The commands \faCenter and \faCenterStyle have been defined to properly center the icons
% when using the default font settings.
%
% You can use any of the icons listed in the fontawesome5 package documentation (https://ctan.math.utah.edu/ctan/tex-archive/fonts/fontawesome5/doc/fontawesome5.pdf)
% If you need to specify a specific style (as is done here for the address card), you should use the two-argument \faCenterCycle command
%
%\begin{center}
%\begin{tabular}{lll}
%	\faCenterStyle{regular}{address-card} Hunan University, Changsha, China 
%	&
%	\faCenter{envelope} \href{mailto:xinh@hnu.edu.cn}{ \color{orange} xinhe9701@gmail.com } 
%	&
%	\faCenter{globe} \href{https://www.xinhesean.com}{ \color{orange} https://www.xinhesean.com}  
%	
%	\\
%	
%	\faCenter{github}  \href{https://github.com/mlfina}{ \color{orange} mlfina}  
%	&
%	\faCenter{google} \href{https://scholar.google.com/citations?user=qD8bY00AAAAJ&hl=en&authuser=2}{ \color{orange}Google Scholar }
%   	&
%	\faCenter{book} \href{https://papers.ssrn.com/sol3/cf_dev/AbsByAuth.cfm?per_id=3071233}{ \color{orange} SSRN } 
%	
%	\\
%\end{tabular}
%\end{center}

\begin{center}
	\begin{tabular}{ll}
		\faCenterStyle{regular}{address-card} {\color{brown} RM 609, BLD 1, IIF USTC, Hefei, China}
		&
		\faCenter{envelope} \href{mailto:xin.he@ustc.edu.cn}{\color{red} \underline{xin.he@ustc.edu.cn}} \\
		\faCenter{globe} \href{https://www.xinhesean.com}{\color{orange} \underline{https://www.xinhesean.com}} 
		&
		% \faCenter{github} \href{https://github.com/xinhe97}{ \color{orange} xinhe97 }  \&  \href{https://github.com/mlfina}{ \color{orange} }   \\
		\faCenter{github}  \href{https://mlfina.github.io/home/}{\color{violet} \underline{MLFINA}}   \\   	
		\faCenter{google} \href{https://scholar.google.com/citations?user=qD8bY00AAAAJ&hl=en&authuser=2}{\color{olive} \underline{Google Scholar}}
		&
		\faCenter{book} \href{https://papers.ssrn.com/sol3/cf_dev/AbsByAuth.cfm?per_id=3071233}{\color{magenta} \underline{SSRN} }          \\
		
	\end{tabular}
\end{center}

%	Last Update: \today

\vspace{-1.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Employment}

\begin{datetabular}{9em}

	\dateentry{2024.08 - }{
	\textbf{University of Science and Technology of China}
	
	\textit{Tenure-Track Associate Professor of Finance, School of Management}
	
	\medskip
	
	\textit{Faculty Affiliate, Faculty of Business for Science and Technology}
	
	\textit{Faculty Affiliate, International Institute of Finance}
	
	}

	\dateentry{2022.09 - 2024.07}{
		\textbf{Hunan University}
		
		\textit{Assistant Professor, College of Finance and Statistics}
	}
	
\end{datetabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

% The datetabular environment takes one argument, which is the width of the left date column. As seen here:
%   9em is a good choice for "dual-date" formats (e.g. Sep 2015 - Nov 2019).
%   4em is a good choice for month/year dates (Sep 2014).
%   2em is a good choice for year-only dates (as seen in the publications)
\begin{datetabular}{9em}
% This is just a tabular environment, for the most part. The dateentry command has been defined for
% convienence. It takes two arguments, the first is the date and the second is whatever you wish placed to the right.
\dateentry{2018 - 2022}{
\textbf{City University of Hong Kong}

\textit{Ph.D. in Management Sciences}

Advisor: Prof. Guanhao Feng, Prof. Junbo Wang
}

\dateentry{2014 - 2018}{
\textbf{Shanghai Jiao Tong University}

\textit{B.S. in Industrial Engineering} 
}

\end{datetabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Interest}
\begin{center}
	Asset Pricing, Quantamental Investment
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publication}

\begin{enumerate}
	\setlength\itemsep{1.0em}
	
%	\item “The Market for English Premier League (EPL) Odds” with Nicholas Polson and Jianeng Xu. Journal of Quantitative Analysis in Sports, 12.4 (2017): 167-178.

	\item “Growing the Efficient Frontier on Panel Trees” 
		with Lin William Cong, Guanhao Feng, and Jingyu He. \\
		\textbf{Journal of Financial Economics}, 2025, 167, 104024. 
		\\
		Award:
			2022 INQUIRE Europe Research Grant Award,
			2024 IQAM Research Prize 
			\\
		Media Coverage: 
			\href{https://mp.weixin.qq.com/s/ePnIBXRj2YE-RSQkoWZTNw}{\underline{FBS}}, 
			\href{https://iif.ustc.edu.cn/2025/0220/c19557a674300/page.htm}{\underline{IIF}}, 
			\href{https://mp.weixin.qq.com/s/rUE0shWHWTzA0EEig2ImCA}{\underline{IIF WeChat}}, 
			\href{https://mp.weixin.qq.com/s/_hwltnHmtVf8iTVh62LhBQ}{\underline{XueShuo}} 
		
	\item “Predicting Individual Corporate Bond Returns” 
		with with Guanhao Feng, Yanchu Wang, and Chunchi Wu. \\
		\textbf{Journal of Banking \& Finance}, 2025, 171, 107372. \\
		Media Coverage: 
			\href{https://mp.weixin.qq.com/s/_hwltnHmtVf8iTVh62LhBQ}{\underline{XueShuo}}
			
	\item “The Bright Side of Cross Ownership: Evidence From the Corporate Resilience to COVID-19 Crisis in China” 
		with Yihui Chen and Haoyuan Wei. \\
		\textbf{International Review of Finance}, 2025, 25(1), e12468.
	
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Working Paper}
\begin{datetabular}{9em}

\dateentry{May 2025}{
	\textbf{Stochastic Discount Factors with Cross-Asset Spillovers}
	\begin{itemize}
		\item with Doron Avramov.
	\end{itemize}\eatvspace}
	
\dateentry{May 2025}{
	\textbf{Panel Tree Benchmarks for Corporate Bond Returns and Mutual Fund Evaluation}
	\begin{itemize}
		\item with Guanhao Feng, Junbo Wang, Chunchi Wu.
	\end{itemize}\eatvspace}
	
\dateentry{Oct. 2024}{
	\textbf{Firm Engagement in Belt and Road Initiative and the Cross-Section of Stock Returns: Evidence from China}
	\begin{itemize}
		\item with Yihui Chen, Jinsheng Liao, and Xiaojuan Wang.
	\end{itemize}\eatvspace}

\dateentry{Oct. 2024}{
	\textbf{The Risk of Finance Words} 
	\begin{itemize}
		\item with Xinbo Chen, and Bowen Du.
	\end{itemize}\eatvspace}

\dateentry{Aug. 2024}{
	\textbf{Benchmarking Individual Corporate Bonds} 
	\begin{itemize}
		\item with Guanhao Feng, Junbo Wang, and Chunchi Wu.
		\item Presented at SoFiE Summer School at NYU SH, CFAM, CIRF, AFBC, NZFM.
	\end{itemize}\eatvspace}

\end{datetabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reference}

\hspace{3cm} \begin{tabular}{l}
	
	\textbf{Guanhao Feng (advisor)}                            \\
	Associate Professor                                  \\
	City University of Hong Kong                \\
	+852 34428346                                      \\
	gavin.feng@cityu.edu.hk                       \\
	
	\\
	
	\textbf{Junye Li}                                   \\
	Professor                                                \\
	Fudan University                                   \\
	+86 25011211                                        \\
	li\_junye@fudan.edu.cn                        \\
	
\end{tabular} \hspace{3cm} \begin{tabular}{l}
	
	\textbf{Jingyu He}                                   \\
	Assistant Professor                                \\
	City University of Hong Kong              \\
	+852 34424753                                    \\
	jingyuhe@cityu.edu.hk                         \\
	
	\\
	
	\textbf{Junbo Wang (advisor)}                              \\
	Professor                                                 \\
	City University of Hong Kong                \\
	+852 34429492                                      \\
	jwang2@cityu.edu.hk                            \\
	
\end{tabular} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grant}

\begin{datetabular}{9em}

\dateentry{2023 - 2025}{
	\textnormal{Co-Investigator, General Research Fund at Hong Kong Research Grants Council} 
		% about 500k HKD 
		\begin{itemize}
			\item with Jingyu He (PI) and Guanhao Feng (Co-I).
			\item Regression Tree for Portfolio Optimization and Imbalanced Data.
		\end{itemize}
	\eatvspace
}

\dateentry{2022 - 2023}{
	\textnormal{Co-Investigator, Research Grant at INQUIRE Europe} 
		% about 10k EURO
		\begin{itemize}
			\item with Jingyu He (PI), Will Cong (Co-I), and Guanhao Feng (Co-I).
			\item Asset Pricing with Panel Tree under Global Split Criteria.
		\end{itemize}
	\eatvspace
}

\dateentry{2022 - 2024}{
	\textnormal{Co-Investigator, General Research Fund at Hong Kong Research Grants Council} 
		% about 700k HKD} 
		\begin{itemize}
			\item with Guanhao Feng (PI), and Junbo Wang (Co-I).
			\item Textual Analysis of Corporate Bond Market.
		\end{itemize}
	\eatvspace
}

\end{datetabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Award}
\begin{datetabular}{9em}
	\dateentry{2024}{IQAM Research Award}
	\dateentry{2024}{Best Paper Award, Session for Corporate Finance and Accounting, 10th Jingshi Scholar Forum, Tsinghua University}
	\dateentry{2023}{Outstanding Advisor for Undergraduate Thesis, Hunan University}
	\dateentry{2022}{INQUIRE Europe Research Grant Award}
	\dateentry{2021}{Best Paper Award, Graduate Student Forum on Economics \& Finance, Antai College, SJTU}
	\dateentry{2021}{College of Business PhD Student Conference Grant, City University of Hong Kong}
	\dateentry{2018-2022}{Ph.D. Studentship, City University of Hong Kong}
	\dateentry{2016}{Second Prize, National Contest of Industrial Engineering Applications, Tsinghua University}
	\dateentry{2015,2016,2017}{Academic Excellence Award, Shanghai Jiao Tong University}
\end{datetabular}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching}
\begin{datetabular}{9em}

\dateentry{USTC}{
	* Students' evaluation in the parentheses.
	\begin{itemize}
		\item Lectures on Financial Engineering and Advanced Topics. 2025 Spring (None)
	\end{itemize}
	\eatvspace
}

\dateentry{Hunan University}{
	\begin{itemize}
		\item Simulation and Experiments in Financial Engineering. 2023 Summer (None)
		\item Fixed-Income Securities. 2023 Autumn (98.00/100)
		\item Behavioral Finance. 2023 Autumn (97.73/100)
	\end{itemize}
	\eatvspace
}

\dateentry{CityU Hong Kong}{
		\begin{itemize}
			\item Tutorial
			\begin{itemize}
				\item Business Statistics. 20/21, 21/22
				\item Statistical Modeling in Finance and Economics. 19/20
			\end{itemize}
			\item Teaching Assistant
			\begin{itemize}
				\item Business Statistics. 21/22
				\item Stochastic Operations Research. 19/20
				\item Statistical Modeling in Marketing. 18/19, 19/20
				\item Statistical Modeling in Finance and Economics. 18/19, 19/20
				\item Operations Management. 18/19
			\end{itemize}
		\end{itemize}
	\eatvspace
}
	
\end{datetabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Service}

\begin{datetabular}{10em}
	
	\dateentry{Ad Hoc Referee}{
	
		Journal of Banking \& Finance,
		Journal of Empirical Finance,
		Journal of Financial Markets,

		Annals of Operations Research, 
		Asia-Pacific Journal of Accounting and Economics, 
		Asia-Pacific Journal of Operations Research, Econometrics and Statistics, 
		Economic Modelling, 
		European Financial Management, 
		Financial Innovation, 
		International Journal of Theoretical and Applied Finance,
		International Review of Finance,
		Journal of Behavioral and Experimental Finance,
		Quantitative Finance,
				
		% Applied Sciences, Econometrics, Economies, Information, International Journal of Financial Studies, Journal of Risk and Financial Management, Sustainability % oa
		
		\eatvspace
		%\vspace{.5cm}
	}

	\dateentry{Conference Organizer}{
	
		\href{https://afc-ustc.org}{\underline{2025 USTC Frontiers in Finance Conference}}
		
		2023 Workshop on Empirical Asset Pricing, College of Finance and Statistics, Hunan University
		
	\eatvspace}
	
	\dateentry{Program Committee}{
		
		2022, 2024 FMA Annual Meeting
		
		\eatvspace
		}
	
	\dateentry{Session Chair}{
		2022 INFORMS Annual Meeting Indianapolis
		\eatvspace}

\end{datetabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Miscellaneous}
\begin{datetabular}{9em}
	\dateentry{Programming}{Python, R, MATLAB, C++, SAS, Linux, SQL, \LaTeX, Microsoft Office}
	\dateentry{Database}{CRSP, Compustat, IBES, TRACE, FISD, Wind, CSMAR}
	\dateentry{Hobby}{Arsenal FC, Sports (fitness, jogging, soccer, basketball, go), Reading (geograghy, philosophy)}
\end{datetabular}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Presentation}

\begin{datetabular}{9em}
	
	\dateentry{2025}{
		\begin{itemize}
			\item EUROFIDAI-ESSEC Paris December Finance Meeting (2025/12, Paris)
			\item USTC Frontiers in Finance Conference, USTC (2025/7, Hefei)
			\item Invited Seminar, School of Management, USTC (2025/6, Hefei)
			\item Hong Kong Conference for Fintech, AI, and Big Data in Business (2025/5, Hong Kong)
			\item Invited Seminar, School of Management, USTC (2025/5, Hefei)
			\item Invited Seminar, Institute for Financial Studies, SWUFE (2025/4, Chengdu)
			\item Annual Meeting of Chinese Statistical Association of Young Scholars (2025/4, Jinan)
			\item Invited Seminar, School of Management, Xiamen University (2025/3, Xiamen)
			\item Invited Seminar, School of Economics, Sichuan University (2025/3, Chengdu)
		\end{itemize}
		\eatvspace
	}
	
	\dateentry{2024}{
		\begin{itemize}
			\item Young Scholar Asset Pricing Workshop, SOE, Xiamen University (2024/10, Xiamen)
			\item Invited Seminar, School of Finance, SWUFE (2024/5, Chengdu)
			\item Invited Seminar, School of Management, USTC (2024/3, Hefei)
		\end{itemize}
		\eatvspace
	}

	\dateentry{2023}{
		\begin{itemize}
			\item Invited Seminar, School of Management, Xiamen University (2023/11, Xiamen)
			\item AI and Big Data in Accounting and Finance Conference, XJTLU  (2023/6, Suzhou)
			\item Financial Econometrics Conference, Lancaster University (2023/3, Lancaster)
		\end{itemize}
		\eatvspace
	}
	
	\dateentry{2022}{
		\begin{itemize}
			\item Australasian Finance \& Banking Conference, UNSW (2022/12, Online)
			\item New Zealand Finance Meeting, AUT (2022/12, Online)
			\item 5th Conference on Big Data, AI, and FinTech, SYSU (2022/11, Online)
			\item China Finance Annual Meeting, SJTU (2022/10, Online) 
			\item China International Risk Forum, DUFE (2022/7, Online)
			\item Asian Meeting of the Econometric Society in China, CUHK(SZ) (2022/6, Online)
			\item 6th PKU-NUS Annual International Conference on Quantitative Finance and Economics, NUS (2022/5, Online)
		\end{itemize}
	\eatvspace
	}

	\dateentry{2021}{
		\begin{itemize}
			\item China Finance Annual Meeting, Xiamen University (2021/10, Online) 
			\item INFORMS Annual Meeting (2021/10, Online) 
			\item Financial Management Association Annual Meeting (2021/10, Online) 
			\item Seminar, City University of Hong Kong (2021/9, Hong Kong) 
			\item SoFiE Financial Econometrics Summer School, NYU SH (2021/8, Online) 
			\item China International Risk Forum, SWUFE (2021/7, Chengdu) 
			\item 37th International Conference of the French Finance Association, Audencia Business School (2021/5, Online) 
			\item 4th China Accounting and Finance Conference, Sichuan University (2021/4, Online) 
			\item Financial Markets and Corporate Governance Conference, La Trobe University (2021/4, Online) 
			\item Camphor Economic Society Seminar Beijing (2021/2, Online) 
			\item Camphor Economic Society Seminar Fujian (2021/1, Online)
		\end{itemize}
	\eatvspace
	}

\end{datetabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

\begin{datetabular}{9em}

	\dateentry{2025}{
	\begin{itemize}
		\item ``Nonverbal Information in Expectation Management -- A Multimodal Perspective (in Chinese)'' at CFRC, Tsinghua University PBCSF, Beijing, China.
		\item ``Oil-Driven Greenium'' at International Conference on Green Finance and ESG, at Southwestern University of Finance and Economics, Chengdu, China.
	\end{itemize}
	\eatvspace
	}
	
	\dateentry{2024}{
	\begin{itemize}
		\item ``Carbon Risk and the Cost of Debt'' at Greater China Area Finance Conference, Xiamen University
		\item ``Investor Sentiment and Cryptocurrency Returns'' at Greater China Area Finance Conference, Xiamen University
	\end{itemize}
	\eatvspace
	}

	\dateentry{2023}{
	\begin{itemize}
		\item ``Do Insurers Listen to Earnings Conference Calls? Evidence from the Corporate Bond Market'' at XJTLU
	\end{itemize}
	\eatvspace
	}

	\dateentry{2022}{
	\begin{itemize}
		\item ``Abnormal Downside Tail Risk as a Predictor of the Risky Bond Returns'' at AFBC
		\item ``Financial Consequences of the Belt and Road Initiative'' at NZFM
		\item ``Air Pollution and Bank Loan Pricing'' at SYSU conference on Big Data, AI, and FinTech
		\item ``Corporate Bond Pricing Using Interpretable and Arbitrage-Free Model'' at CIRF
		\end{itemize}
	\eatvspace
	}

	\dateentry{2021}{
		\begin{itemize}
			\item ``Manager Uncertainty and the Cross-Section of Stock Returns'' at FMA
			\item ``Does Reputation Matter? Evidence on Spatial Competition in China’s Bond Market" at FMCG
		\end{itemize}
	\eatvspace
	}

	\dateentry{2020}{
		\begin{itemize}
			\item ``How should we measure the performance of corporate bond mutual funds? Evaluating model quality and impact on inferences'' at FMA
		\end{itemize}
	\eatvspace
	}

\end{datetabular}

\begin{center}
	Last Update: \today
\end{center}
	
\end{document}
