\documentclass{clean_cv}

\usepackage{etaremune}
\usepackage[fontset=fandol]{ctex}

\author{Xin He}
\headlineposition{}

\begin{document}

\maketitle

\begin{center}
	\begin{tabular}{ll}
		\faCenterStyle{regular}{address-card} {\color{brown} 中国合肥市中国科学技术大学国际金融研究院 1 号楼 609 室}
		&
		\faCenter{envelope} \href{mailto:xin.he@ustc.edu.cn}{\color{red} \underline{xin.he@ustc.edu.cn}} \\
		\faCenter{globe} \href{https://www.xinhesean.com}{\color{orange} \underline{https://www.xinhesean.com}}
		&
		\faCenter{github} \href{https://mlfina.github.io/home/}{\color{violet} \underline{MLFINA}} \\
		\faCenter{google} \href{https://scholar.google.com/citations?user=qD8bY00AAAAJ&hl=en&authuser=2}{\color{olive} \underline{Google Scholar}}
		&
		\faCenter{book} \href{https://papers.ssrn.com/sol3/cf_dev/AbsByAuth.cfm?per_id=3071233}{\color{magenta} \underline{SSRN}} \\
	\end{tabular}
\end{center}

\vspace{-1.5em}

\section{工作经历}

\begin{datetabular}{9em}

	\dateentry{2024.08 -- 至今}{
	\textbf{中国科学技术大学}

	\textit{科技商学院、管理学院金融学特任副教授}

	}

	\dateentry{2022.09 -- 2024.07}{
		\textbf{湖南大学}

		\textit{金融与统计学院助理教授}
	}

\end{datetabular}

\section{教育背景}

\begin{datetabular}{9em}
\dateentry{2018 -- 2022}{
\textbf{香港城市大学}

\textit{管理科学博士}

导师：冯冠豪教授、王军波教授
}

\dateentry{2014 -- 2018}{
\textbf{上海交通大学}

\textit{工业工程学士}
}

\end{datetabular}

\section{研究方向}
\begin{center}
	资产定价，金融计量，机器学习，量化投资，中国资本市场
\end{center}

\section{发表论文}

\begin{enumerate}
	\setlength\itemsep{1.0em}

	\item ``Growing the Efficient Frontier on Panel Trees''
		with Lin William Cong, Guanhao Feng, and Jingyu He. \\
		\textbf{Journal of Financial Economics}, 2025, 167, 104024.
		\\
		奖励：
			2022 INQUIRE Europe Research Grant Award，
			2024 IQAM Research Prize
			\\
		媒体报道：
			\href{https://mp.weixin.qq.com/s/ePnIBXRj2YE-RSQkoWZTNw}{\underline{FBS}}，
			\href{https://iif.ustc.edu.cn/2025/0220/c19557a674300/page.htm}{\underline{IIF}}，
			\href{https://mp.weixin.qq.com/s/rUE0shWHWTzA0EEig2ImCA}{\underline{IIF WeChat}}，
			\href{https://mp.weixin.qq.com/s/_hwltnHmtVf8iTVh62LhBQ}{\underline{学说}}，
			\href{http://thfr.com.cn/magazine_detail.php?id=149}{\underline{清华金融评论}}。

	\item ``Predicting Individual Corporate Bond Returns''
		with Guanhao Feng, Yanchu Wang, and Chunchi Wu. \\
		\textbf{Journal of Banking \& Finance}, 2025, 171, 107372. \\
		媒体报道：
			\href{https://mp.weixin.qq.com/s/_hwltnHmtVf8iTVh62LhBQ}{\underline{学说}}。

	\item ``The Bright Side of Cross Ownership: Evidence From the Corporate Resilience to COVID-19 Crisis in China''
		with Yihui Chen and Haoyuan Wei. \\
		\textbf{International Review of Finance}, 2025, 25(1), e12468.

\end{enumerate}

\section{工作论文}
\begin{datetabular}{9em}

\dateentry{2026 年 2 月}{
	\textbf{Stochastic Discount Factors with Cross-Asset Spillovers}
	\begin{itemize}
		\item 与 Doron Avramov 合作。
		\item 奖励：2025 INQUIRE Europe Research Grant Award；2025 中山大学 Conference on Big Data, AI, and FinTech 最佳论文奖。
	\end{itemize}\eatvspace}

\dateentry{2026 年 1 月}{
	\textbf{Optimal Portfolios with Trading Costs: The Case of Asset Spillovers}
\eatvspace}

\dateentry{2026 年 3 月}{
	\textbf{Generative Portfolio Optimization with Transaction Cost: A Panel Tree Method}
\eatvspace}

\dateentry{2026 年 2 月}{
	\textbf{Factor Investing and the Integration of Equity and Corporate Bond Markets}
\eatvspace}

\dateentry{2026 年 1 月}{
	\textbf{Panel Tree Benchmarks for Corporate Bond Returns and Mutual Fund Evaluation}
\eatvspace}

\dateentry{2026 年 1 月}{
	\textbf{Corporate Bond Pricing via Panel Trees}
\eatvspace}

\dateentry{2025 年 7 月}{
	\textbf{AI Applications and the Opportunistic Insider Trading of Executives: Evidence from China}
	\begin{itemize}
		\item 与 Shuqi Zhang、Along Liu、Jibao Gu 合作。
		\item 修改后投回。
	\end{itemize}
\eatvspace}

\dateentry{2025 年 11 月}{
	\textbf{When Competitors Go Public: Innovation Spillovers through Competitive Pressure and Learning Channels}
	\begin{itemize}
		\item 与 Yihui Chen、Zeyi Wu、Zhilin Wu 合作。
		\item 修改后投回。
	\end{itemize}
\eatvspace}

\dateentry{2024 年 10 月}{
	\textbf{The Risk of Finance Words}
	\begin{itemize}
		\item 与 Xinbo Chen、Bowen Du 合作。
		\item 修改后投回。
	\end{itemize}\eatvspace}

\dateentry{2024 年 10 月}{
	\textbf{Firm Engagement in Belt and Road Initiative and the Cross-Section of Stock Returns: Evidence from China}
	\begin{itemize}
		\item 与 Yihui Chen、Jinsheng Liao、Xiaojuan Wang 合作。
	\end{itemize}\eatvspace}

\end{datetabular}

\section{推荐人}

\hspace{3cm} \begin{tabular}{l}

	\textbf{冯冠豪} \\
	副教授 \\
	香港城市大学 \\
	+852 34428346 \\
	gavin.feng@cityu.edu.hk \\

	\\

	\textbf{李隽业} \\
	讲席教授 \\
	复旦大学 \\
	+86 25011211 \\
	li\_junye@fudan.edu.cn \\

\end{tabular} \hspace{3cm} \begin{tabular}{l}

	\textbf{何靖宇} \\
	副教授 \\
	香港城市大学 \\
	+852 34424753 \\
	jingyuhe@cityu.edu.hk \\

	\\

	\textbf{王军波} \\
	教授 \\
	香港城市大学 \\
	+852 34429492 \\
	jwang2@cityu.edu.hk \\

\end{tabular}

\section{科研项目}

\begin{datetabular}{9em}

\dateentry{2026 -- 2026}{
	\textbf{主持}，\textnormal{中国科学技术大学青年创新基金}
		\begin{itemize}
			\item Cross-Predictability in Empirical Asset Pricing: Theory and Evidence.
		\end{itemize}
	\eatvspace
}

\dateentry{2026 -- 2026}{
	\textbf{主持}，\textnormal{中国科学技术大学 Global Initiative Fund}
		\begin{itemize}
			\item Pricing Corporate Bond Returns with Panel Tree.
		\end{itemize}
	\eatvspace
}

\dateentry{2023 -- 2025}{
	\textnormal{参与，香港研究资助局 General Research Fund}
		\begin{itemize}
			\item 与 Jingyu He（PI）及 Guanhao Feng（Co-I）合作。
			\item Regression Tree for Portfolio Optimization and Imbalanced Data.
		\end{itemize}
	\eatvspace
}

\dateentry{2022 -- 2024}{
	\textnormal{参与，香港研究资助局 General Research Fund}
		\begin{itemize}
			\item 与 Guanhao Feng（PI）及 Junbo Wang（Co-I）合作。
			\item Textual Analysis of Corporate Bond Market.
		\end{itemize}
	\eatvspace
}

\end{datetabular}

\section{荣誉奖励}
\begin{datetabular}{9em}
	\dateentry{2025}{中山大学 Conference on Big Data, AI, and FinTech 最佳论文奖}
	\dateentry{2025}{INQUIRE Europe Research Grant Award}
	\dateentry{2024}{IQAM Research Award}
	\dateentry{2024}{清华大学第十届经世学者论坛公司金融与会计分会场最佳论文奖}
	\dateentry{2023}{湖南大学本科毕业论文优秀指导教师}
	\dateentry{2022}{INQUIRE Europe Research Grant Award}
	\dateentry{2021}{上海交通大学安泰经济与金融研究生论坛最佳论文奖}
	\dateentry{2021}{香港城市大学商学院博士生会议资助}
	\dateentry{2018--2022}{香港城市大学博士奖学金}
	\dateentry{2016}{清华大学全国工业工程应用案例大赛二等奖}
	\dateentry{2015, 2016, 2017}{上海交通大学学业优秀奖}
\end{datetabular}

\section{教学经历}
\begin{datetabular}{9em}

\dateentry{中国科大}{
	* 括号内为学生评教分数。
	\begin{itemize}
		\item 实证资产定价，金融硕士，2026 年春季学期（暂无）
		\item 实证资产定价，学术硕士，2026 年春季学期（暂无）
		\item 金融机构与金融市场，本科，2026 年春季学期（暂无）
		\item 金融工程与前沿专题讲座，2025 年春季学期（暂无）
	\end{itemize}
	\eatvspace
}

\dateentry{湖南大学}{
	\begin{itemize}
		\item 金融工程模拟与实验，2023 年夏季学期（暂无）
		\item 固定收益证券，2023 年秋季学期（98.00/100）
		\item 行为金融学，2023 年秋季学期（97.73/100）
	\end{itemize}
	\eatvspace
}

\dateentry{高校与金融机构}{
		\begin{itemize}
			\item 客座报告：资产定价与量化投资
		\end{itemize}
	\eatvspace
}

\end{datetabular}

\section{学术服务}

\begin{datetabular}{10em}

	\dateentry{匿名审稿}{

		Management Science,
		Journal of Banking \& Finance,
		Journal of Empirical Finance,
		Journal of Finance and Data Science,
		Journal of Financial Econometrics,
		Journal of Financial Markets,
		Annals of Operations Research,
		Asia-Pacific Journal of Accounting and Economics,
		Asia-Pacific Journal of Operations Research,
		Econometrics and Statistics,
		Economic Modelling,
		European Financial Management,
		Financial Innovation,
		Financial Research Letters,
		International Journal of Finance \& Economics,
		International Journal of Theoretical and Applied Finance,
		International Review of Finance,
		Journal of Behavioral and Experimental Finance,
		Journal of International Financial Markets, Institutions \& Money,
		Quantitative Finance,
		Review of Managerial Science.

		\eatvspace
	}

	\dateentry{会议组织}{

		\href{https://afc-ustc.org}{\underline{2025 USTC Frontiers in Finance Conference}}

		2023 湖南大学金融与统计学院实证资产定价工作坊

	\eatvspace}

	\dateentry{程序委员会}{

		2022, 2024 FMA Annual Meeting

		\eatvspace
		}

	\dateentry{分会主持}{
		2022 INFORMS Annual Meeting, Indianapolis
		\eatvspace}

\end{datetabular}

\section{其他信息}
\begin{datetabular}{9em}
	\dateentry{编程}{Python, R, MATLAB, C++, SAS, Linux, SQL, \LaTeX, Microsoft Office}
	\dateentry{数据库}{CRSP, Compustat, IBES, TRACE, FISD, Wind, CSMAR}
	\dateentry{兴趣}{阿森纳足球俱乐部，运动（健身、慢跑、足球、篮球、围棋），阅读（地理、哲学）}
\end{datetabular}

\section{学术报告}

\begin{datetabular}{9em}

	\dateentry{2026}{
		\begin{itemize}
			\item 邀请报告，清华大学五道口金融学院（2026/4，北京）
			\item Hong Kong Conference on Fintech and AI in Finance（2026/6，香港）
		\end{itemize}
		\eatvspace
	}

	\dateentry{2025}{

EUROFIDAI-ESSEC Paris December Finance Meeting（2025/12，巴黎）；复旦大学 AI in Finance 国际研讨会（2025/11，上海）；中山大学 Conference on Big Data, AI, and FinTech（2025/10，广州）；澳门大学 FinTech and Financial Markets Workshop（2025/10，澳门）；邀请报告，上海交通大学安泰经管学院（2025/10，上海）；邀请业界报告，AITOPIA（2025/7，线上）；USTC Frontiers in Finance Conference（2025/7，合肥）；邀请报告，中国科学技术大学管理学院（2025/6，合肥）；Hong Kong Conference for Fintech, AI, and Big Data in Business（2025/5，香港）；邀请报告，中国科学技术大学管理学院（2025/5，合肥）；邀请报告，西南财经大学金融研究所（2025/4，成都）；中国青年统计学者年会（2025/4，济南）；邀请报告，厦门大学管理学院（2025/3，厦门）；邀请报告，四川大学经济学院（2025/3，成都）

		\eatvspace
	}

	\dateentry{2024}{

青年学者资产定价研讨会，厦门大学经济学院（2024/10，厦门）；邀请报告，西南财经大学金融学院（2024/5，成都）；邀请报告，中国科学技术大学管理学院（2024/3，合肥）

		\eatvspace
	}

	\dateentry{2023}{

		 邀请报告，厦门大学管理学院（2023/11，厦门）；
		 AI and Big Data in Accounting and Finance Conference，西交利物浦大学（2023/6，苏州）；
		Financial Econometrics Conference，Lancaster University（2023/3，Lancaster）

		\eatvspace
	}

	\dateentry{2022}{

			Australasian Finance \& Banking Conference，UNSW（2022/12，线上）；
			 New Zealand Finance Meeting，AUT（2022/12，线上）；
			 第五届 Conference on Big Data, AI, and FinTech，中山大学（2022/11，线上）；
			 China Finance Annual Meeting，上海交通大学（2022/10，线上）；
			 China International Risk Forum，东北财经大学（2022/7，线上）；
			 Asian Meeting of the Econometric Society in China，香港中文大学（深圳）（2022/6，线上）；
			 第六届 PKU-NUS Annual International Conference on Quantitative Finance and Economics，新加坡国立大学（2022/5，线上）

	\eatvspace
	}

	\dateentry{2021}{

			China Finance Annual Meeting，厦门大学（2021/10，线上）；
			INFORMS Annual Meeting（2021/10，线上）；
			Financial Management Association Annual Meeting（2021/10，线上）；
			讲座，香港城市大学（2021/9，香港）；
			SoFiE Financial Econometrics Summer School，NYU Shanghai（2021/8，线上）；
			China International Risk Forum，西南财经大学（2021/7，成都）；
			第 37 届 French Finance Association 国际会议，Audencia Business School（2021/5，线上）；
			第四届 China Accounting and Finance Conference，四川大学（2021/4，线上）；
			Financial Markets and Corporate Governance Conference，La Trobe University（2021/4，线上）；
			Camphor Economic Society Seminar Beijing（2021/2，线上）；
			Camphor Economic Society Seminar Fujian（2021/1，线上）

	\eatvspace
	}

\end{datetabular}

\section{论文讨论}

\begin{datetabular}{9em}

	\dateentry{2025}{
	\begin{itemize}
		\item ``Deciphering the Impact of BigTech Consumer Credit''，Conference on Big Data, AI, and FinTech，中山大学，广州。
		\item ``Nonverbal Information in Expectation Management -- A Multimodal Perspective (in Chinese)''，CFRC，清华大学五道口金融学院，北京。
		\item ``Oil-Driven Greenium''，International Conference on Green Finance and ESG，西南财经大学，成都。
	\end{itemize}
	\eatvspace
	}

	\dateentry{2024}{
	\begin{itemize}
		\item ``Carbon Risk and the Cost of Debt''，Greater China Area Finance Conference，厦门大学
		\item ``Investor Sentiment and Cryptocurrency Returns''，Greater China Area Finance Conference，厦门大学
	\end{itemize}
	\eatvspace
	}

	\dateentry{2023}{
	\begin{itemize}
		\item ``Do Insurers Listen to Earnings Conference Calls? Evidence from the Corporate Bond Market''，西交利物浦大学会议
	\end{itemize}
	\eatvspace
	}

	\dateentry{2022}{
	\begin{itemize}
		\item ``Abnormal Downside Tail Risk as a Predictor of the Risky Bond Returns''，AFBC
		\item ``Financial Consequences of the Belt and Road Initiative''，NZFM
		\item ``Air Pollution and Bank Loan Pricing''，SYSU Conference on Big Data, AI, and FinTech
		\item ``Corporate Bond Pricing Using Interpretable and Arbitrage-Free Model''，CIRF
		\end{itemize}
	\eatvspace
	}

	\dateentry{2021}{
		\begin{itemize}
			\item ``Manager Uncertainty and the Cross-Section of Stock Returns''，FMA
			\item ``Does Reputation Matter? Evidence on Spatial Competition in China’s Bond Market''，FMCG
		\end{itemize}
	\eatvspace
	}

	\dateentry{2020}{
		\begin{itemize}
			\item ``How should we measure the performance of corporate bond mutual funds? Evaluating model quality and impact on inferences''，FMA
		\end{itemize}
	\eatvspace
	}

\end{datetabular}

\begin{center}
	最后更新：2026 年 3 月 18 日
\end{center}

\end{document}
